---
title: "newest dataset world gender statsitics 2021"
author: "Linda Sinani"
date: "4 7 2021"
output: html_document
---

```{r setup, include=FALSE}

library(ggplot2)
library(tidyr)
library(dplyr)

knitr::opts_chunk$set(echo = TRUE)
```

## Bereich Arbeit 
Nachfolgend ein Auszug aus dem riesigen World Gender Statistics Datensatz. 
Der Datensatz bezieht sich auf den Unterschied zwischen den Geschlechtern nur in Deutschland im Bereich Arbeit. 



### Datensatz aufräumen
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(digits = 2)
gender_arbeit_DL <- readr::read_csv(file = "data/bereich_arbeit_deutschland_gender_statsitics.csv")

is.numeric(gender_arbeit_DL$`2000 [YR2000]`)

gender_arbeit_DL$`1983 [YR1983]` <- as.numeric(gender_arbeit_DL$`1983 [YR1983]`)
gender_arbeit_DL$`1984 [YR1984]` <- as.numeric(gender_arbeit_DL$`1984 [YR1984]`)
gender_arbeit_DL$`1985 [YR1985]` <- as.numeric(gender_arbeit_DL$`1985 [YR1985]`)
gender_arbeit_DL$`1986 [YR1986]` <- as.numeric(gender_arbeit_DL$`1986 [YR1986]`)
gender_arbeit_DL$`1987 [YR1987]` <- as.numeric(gender_arbeit_DL$`1987 [YR1987]`)
gender_arbeit_DL$`1988 [YR1988]` <- as.numeric(gender_arbeit_DL$`1988 [YR1988]`) 
gender_arbeit_DL$`1989 [YR1989]` <- as.numeric(gender_arbeit_DL$`1989 [YR1989]`)
gender_arbeit_DL$`1990 [YR1990]` <- as.numeric(gender_arbeit_DL$`1990 [YR1990]`)
gender_arbeit_DL$`1991 [YR1991]` <- as.numeric(gender_arbeit_DL$`1991 [YR1991]`)
gender_arbeit_DL$`1992 [YR1992]` <- as.numeric(gender_arbeit_DL$`1992 [YR1992]`)
gender_arbeit_DL$`1993 [YR1993]` <- as.numeric(gender_arbeit_DL$`1993 [YR1993]`)
gender_arbeit_DL$`1994 [YR1994]` <- as.numeric(gender_arbeit_DL$`1994 [YR1994]`)
gender_arbeit_DL$`1995 [YR1995]` <- as.numeric(gender_arbeit_DL$`1995 [YR1995]`)
gender_arbeit_DL$`1996 [YR1996]` <- as.numeric(gender_arbeit_DL$`1996 [YR1996]`)
gender_arbeit_DL$`1997 [YR1997]` <- as.numeric(gender_arbeit_DL$`1997 [YR1997]`)
gender_arbeit_DL$`1998 [YR1998]` <- as.numeric(gender_arbeit_DL$`1998 [YR1998]`)
gender_arbeit_DL$`1999 [YR1999]` <- as.numeric(gender_arbeit_DL$`1999 [YR1999]`)

gender_arbeit_DL <- data.frame(t(gender_arbeit_DL))
gender_arbeit_DL <- gender_arbeit_DL[-c(2,3,4), -c(32:36)]

write.csv(gender_arbeit_DL, "data/gender_arbeit_DL.csv")
```


## Erklärung Variablen
"Employers, female (% of female employment) (modeled ILO estimate)"
"Employers, male (% of male employment) (modeled ILO estimate)"
"Employers, total (% of total employment) (modeled ILO estimate)"
"Employment in agriculture (% of total employment) (modeled ILO estimate)"
"Employment in agriculture, female (% of female employment) (modeled ILO estimate)"
"Employment in agriculture, male (% of male employment) (modeled ILO estimate)"
"Employment in industry (% of total employment) (modeled ILO estimate)"
"Employment in industry, female (% of female employment) (modeled ILO estimate)"
"Employment in industry, male (% of male employment) (modeled ILO estimate)"
"Employment in services (% of total employment) (modeled ILO estimate)"
"Employment in services, female (% of female employment) (modeled ILO estimate)"
"Employment in services, male (% of male employment) (modeled ILO estimate)"
"Female share of employment in senior and middle management (%)"
"Law prohibits discrimination in employment based on gender (1=yes; 0=no)"
"Part time employment, female (% of total part time employment)"
"Part time employment, male (% of total male employment)"
"Part time employment, total (% of total employment)","Self-employed, female (% of female employment) (modeled ILO estimate)"
"Self-employed, male (% of male employment) (modeled ILO estimate)"
"Self-employed, total (% of total employment) (modeled ILO estimate)"
"There is legislation on sexual harassment in employment (1=yes; 0=no)"
"Unemployment, female (% of female labor force) (modeled ILO estimate)"
"Unemployment, female (% of female labor force) (national estimate)"
"Unemployment, male (% of male labor force) (modeled ILO estimate)"
"Unemployment, male (% of male labor force) (national estimate)","Unemployment, total (% of total labor force) (modeled ILO estimate)"
"Unemployment, total (% of total labor force) (national estimate)"
"Wage and salaried workers, female (% of female employment) (modeled ILO estimate)"
"Wage and salaried workers, male (% of male employment) (modeled ILO estimate)"
"Wage and salaried workers, total (% of total employment) (modeled ILO estimate)"
"Criminal penalties or civil remedies exist for sexual harassment in employment (1=yes; 0=no)"